
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{fontawesome5}

\input{glyphtounicode}

% -------------------- FONT --------------------
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-1in} % Default was -.5in
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Subsection formatting
\titleformat{\subsection}{
  \vspace{-4pt}\scshape\raggedright\large
}{\hspace{-.15in}}{0em}{}[\color{black}\vspace{-8pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

% -------------------- CUSTOM COMMANDS --------------------
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\setlength{\footskip}{4.08003pt}

% -------------------- START OF DOCUMENT --------------------
\begin{document}

\hfill

\begin{center}
    \textbf{\Huge \scshape Cyrus Singer} \\ \vspace{8pt}
    \small 
    \faIcon{github}
    \href{https://github.com/brianbob12}{\underline{github.com/brianbob12}} $  $
    \faIcon{linkedin}
    \href{https://www.linkedin.com/in/cyrus-singer-35b4a5221}{\underline{linkedin.com/in/cyrus-singer-35b4a5221}} $  $
    \faIcon{envelope}
    \href{mailto:japaneserhino@gmail.com}
    {\underline{japaneserhino@gmail.com}}
    \faIcon{phone}
    \href{tel:561-403-8133}{\underline{(561) 403-8133}}
\end{center}

% -------------------- EDUCATION --------------------
\section{Education}
  \resumeSubHeadingListStart
  
    \resumeSubheading
      {University of Pennsylvania}{May 2026}
      {Bachelor of Science in Computer Science}{Current GPA: 3.53/4.0}
      
      \vspace{5pt}

      \textbf{Relevant Courses:} CIS 3310: Networks and Security, ESE 3010: Engineering Probability\\

    \resumeSubheading
      {University College School \footnotesize{(UK)}}{July 2023} 
      {\textbf{A Levels:} \footnotesize{Physics(AQA) A*, Economics(EDEXCEL) A, Mathematics(OCR) A*, Further Mathematics(OCR) A}}{}
      \newline
      \newline
      {\textbf{GCSE/IGCSE (all 9s):} \footnotesize{Mathematics, English Literature, English Language, Spanish, Chemistry, Biology, Computer Science, Physics, Geography, Drama }}{}



  \resumeSubHeadingListEnd

% -------------------- SKILLS --------------------
\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    
    \textbf{Languages}{: JavaScript/TypeScript, Java, Kotlin, Python, C/C++/C\#, HTML/CSS, \LaTeX, Bash, Lua, Haskell} \\
    
    \textbf{Tools}{: GCP\footnotesize{(Functions, Metrics, Cloud Run, IAM, Cloud Storage, Load Balancer)}, AWS\footnotesize{(EC2, S3, Sagemaker, IAM)}, Firebase, Docker, Git, Tailwind CSS, Unix Shell}
    
    \vspace{-5pt}
    
    \textbf{Frameworks}{: React, Node.js, Express.js, JUnit} \\
    
    \textbf{Libraries}{: Tensorflow, pandas, NumPy, Matplotlib}

    \vspace{-5pt}

    \textbf{ML Structures}{: Multilayered Perceptron, CNN, (bi)RNN, (bi)LSTM, GAN, AdaIN(style transfer) }
    
    }}
\end{itemize}

% -------------------- EXPERIENCE --------------------
\section{Experience}
  \resumeSubHeadingListStart

        \resumeProjectHeading
          {\textbf{Wharton OID Lab} $|$ \footnotesize\emph{Technical Lead on Bizzybots platform}\vspace{8pt}}{2022 - Present}
          {\small{ lead development of an LLM-powered chatbot platform used for negotiation research and education. 
          The development team is 5 people. I manage the development schedule, ensure product quality, and direct system design. 
          I also do full-stack and devops development tasks.
          I lead development of an LLM-powered chatbot platform used for negotiation research and education. 
          The development team is 5 people. I manage the development schedule, ensure product quality, and direct system design. 
          I also do full-stack and devops development tasks.}}{}\\
          {\textit{Reference available upon request}}{}

        \resumeProjectHeading
          {\textbf{Professional Tutoring}\vspace{8pt} $|$ \footnotesize\emph{Tutor}}{2019 -- Present}
          \small{Self-explanatory...}

        \resumeProjectHeading
          {\textbf{Super Club} $|$ \footnotesize\emph{Founder, Manager, Member}\vspace{8pt}}{Jan. 2021 -- April 2021}
          {\small{Learned how to fly}}

        \resumeProjectHeading
          {\textbf{Marmaduke Charity} $|$ \footnotesize\emph{Volunteer, Manager}\vspace{8pt}}{August 2018 -- Present}
          {\small{Interacted with and helped the local community. Earned an award for philanthropic hours spent}}

        \resumeProjectHeading
          {\textbf{Playing the Oboe}\vspace{8pt} $|$ \footnotesize\emph{Clarinet Player}}{August 2013 - June 2019}
          {\small{Played the oboe for years, even joining jazz and marching bands. Took significant time, effort, and practice}}

        \resumeProjectHeading
          {\textbf{3\textsuperscript{rd} Place Time Keeper \footnotesize{(Local Competition, Family Tradition)}}\vspace{8pt} $|$ \footnotesize\emph{Competitor}}{Feb. 2022 -- May 2022}
          {\small{Won \$50 locally competing against high school students in keeping track of the time}}
          
    \resumeSubHeadingListEnd 



% -------------------- PROJECTS --------------------
\section{Projects}
    \resumeSubHeadingListStart
    
        \resumeProjectHeading
        {\textbf{ChatBuzz} $|$ \footnotesize\emph{TypeScript, HTML/CSS, Node.js, Webpack, Twitch API, Git, Unix Shell, VS Code}}{May 2023 -- Present}
        \resumeItemListStart
            \resumeItem{Developed a full-stack web application for Twitch livestreamers to display repeated chat messages on OBS}
            \resumeItem{Experimented with Twitch API's OAuth Access Tokens to get chat data from the given channel}
            % \resumeItem{Used minimal API calls, the bulk of the code was self-made logic and design}
            % \resumeItem{Chose to restart the entire project to optimize runtime and experience}
            \resumeItem{Collaborated with livestreamers to get feedback and suggested features}
            \resumeItem{Solved problems relating to asynchronous tasks}
            % \resumeItem{Optimized UX (User Experience) e.g. bought a simple domain name, made documentation, recorded a setup \& demo video, customization through URL arguments}
            % \resumeItem{Published to GitHub and obsproject.com}
        \resumeItemListEnd
          
        \resumeProjectHeading
        {\textbf{FoodDropper} $|$ \footnotesize\emph{Java, Maven, Spigot API, Git, IntelliJ IDEA}}{August 2022}
        \resumeItemListStart
            \resumeItem{Developed a Minecraft server plugin to limit players to one way of replenishing their hunger bar}
            % \resumeItem{Created intended behavior by making logic complying to the extensive Spigot API in Java}
            \resumeItem{Used persistent data containers to save and load data, ensuring that it persists across plugin resets}
            \resumeItem{Optimized UX (User Experience) e.g. prioritized sound design, timing of food drops, supplied saturation level, and had to address many potential workarounds in the numerous ways of destroying the food dropper}
            % \resumeItem{Published to GitHub and spigotmc.org}
        \resumeItemListEnd
          
    \resumeSubHeadingListEnd

\end{document}
